### 2016-10-17 R/ITHIM.Rmd
Tweaked figure 1
Made a few changes to get running on new iMac

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
library("dplyr")
library("cowplot")
library("grid")
library("scales")
library("ggthemes")
```

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
library("devtools")
install_github("smbache/magrittr", ref="master")
library("magrittr")
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="devel")
library("ITHIM")

@@

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(45, 120, length.out = 5)
muNonTravelVec <- c(1,10,25)
DTotal <- data.frame()

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
# install.packages(c("knitr","ggplot2","dplyr","openssl","httr", "git2r","devtools"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
#library("cowplot")
#library("grid")
#library("scales")
#library("ggthemes")
```

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

library("magrittr")
library("ITHIM")

@@

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(45, 120, length.out = 5)
muNonTravelVec <- c(1,5,10,25)
DTotal <- data.frame()
